\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5} % For icons

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1\vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeProjectHeading}[3]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} \href{#3}{\raisebox{-0.2\height}\faGithub\ GitHub} & \textbf{#2}\\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Navneet Pathak} \\ \vspace{2pt}
    \small
    \href{tel:+918923651177}{\raisebox{-0.1\height}\faPhone\ +91-8923651177} \quad
    \href{mailto:navneetpathak1909@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ navneetpathak1909@gmail.com} \quad
    \href{https://github.com/navneetpathak1}{\raisebox{-0.2\height}\faGithub\ GitHub} \quad
    \href{https://leetcode.com/navendupandey_14}{\raisebox{-0.2\height}\faLaptopCode\ LeetCode}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Graphic Era Hill University, Bhimtal}{2022 -- 2026}
    {Bachelor of Technology (B.Tech) in Computer Science and Engineering}{}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {Digital Wallet Platform (React.js, Express.js, MongoDB, Tailwind CSS)}{}{https://github.com/navneetpathak1/Payment_app}
    \resumeItemListStart
      \resumeItem{Developed a peer-to-peer (P2P) payment application enabling users to transfer virtual currency securely.}
      \resumeItem{Implemented authentication, user management, transaction history, and protected routes.}
      \resumeItem{Applied REST APIs and JWT for secure backend communication and data security.}
    \resumeItemListEnd

  \resumeProjectHeading
    {Real-Time Chat Application (MERN Stack, Socket.IO, Tailwind CSS)}{}{https://github.com/navneetpathak1/Real-time-chat-app}
    \resumeItemListStart
      \resumeItem{Built a multi-user messaging platform supporting real-time chat using WebSockets and Socket.IO.}
      \resumeItem{Designed and deployed a mobile-responsive UI; features include typing indicators and live messaging.}
      \resumeItem{Deployed backend with Node.js and MongoDB Atlas for scalability and high availability.}
    \resumeItemListEnd

  \resumeProjectHeading
    {Udemy-Like Online Learning System (MERN Stack)}{}{https://github.com/navneetpathak1/New-Project}
    \resumeItemListStart
      \resumeItem{Created a course management system supporting course creation, purchase, and video content streaming.}
      \resumeItem{Integrated secure payment gateway using Stripe APIs; optimized MongoDB queries for fast access.}
      \resumeItem{Built protected admin and user dashboards for course tracking and management.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Programming Languages:} C, C++, JavaScript (ES6+), SQL
    \item \textbf{Frameworks/Libraries:} React.js, Express.js, Node.js, Socket.IO, Tailwind CSS
    \item \textbf{Databases:} MongoDB, PostgreSQL, MySQL
    \item \textbf{Cloud/Tools:} AWS, Postman, Git, GitHub, Prisma ORM
    \item \textbf{Concepts:} Data Structures and Algorithms (DSA), REST APIs, Agile Development, Software Engineering Principles
\end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications}
\resumeSubHeadingListStart

  \resumeSubheading
    {Generative AI Learning Plan for Developers}{Apr 2025}
    {Amazon Web Services (AWS)}{}

  \resumeSubheading
    {AWS Artificial Intelligence Practitioner Learning Plan}{Apr 2025}
    {Amazon Web Services (AWS)}{}

  \resumeSubheading
    {DevOps Engineer Learning Plan (includes Labs)}{Apr 2025}
    {Amazon Web Services (AWS)}{}

  \resumeSubheading
    {Cloud Operator (SysOps) Learning Plan}{Apr 2025}
    {Amazon Web Services (AWS)}{}

  \resumeSubheading
    {Advanced Software Engineering Virtual Experience}{Apr 2025}
    {Walmart USA - Forage Platform}{}
    \resumeItemListStart
      \resumeItem{Completed real-world simulations in Data Structures, Software Architecture, and Database Design.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}
